% Documentation for Tic Tac Toe in C++, Mateusz Bysiek 2010

\documentclass{article}
\usepackage{color}
\usepackage{enumerate}
\usepackage[empty]{fullpage} %small margins
\usepackage[pdftex]{graphicx} %pictures

\begin{document}

\title{Tic Tac Toe – documentation addon}
\author{Mateusz Bysiek}
\maketitle

\section{Player's guide}

Author assumes that user is familliar with rules of ordinary Tic Tac Toe game.

\begin{enumerate}
\item Enter the exact same hostname and port as in server instance.
\item Enter some nickname and password. Check 'create new' box.
\item Click join. When a 2nd player joins, the game will start.
\item When a game finishes, you can play once more by selecting the proper option in the game's window menu.
\end{enumerate}

More info soon.

\section{Admin's guide}

More info soon.

\section{Developer's guide}

\subsection{List of xml messages types}

\paragraph{systemmsg} sent by both clients and server
\paragraph{chatmsg} sent by clients
\paragraph{game} sent by server to all clients at the same time
\paragraph{celldata} sent by a client that just made a move
\paragraph{participant} sent by client when logging in to the server

\subsection{System messages sent by clients to server}

\paragraph{pong} response for ping
\paragraph{permissionToCreate} signals that there was permission given to create account in case that username is free
\paragraph{turnend} signals that player made the move
\paragraph{onemoregame} signals that player wants to play one more game
\paragraph{incPlayed} signals that player received result of the game (and it was draw or his defeat)
\paragraph{incWin} signals that player received result of the game (and he won)

\subsection{System messages sent by server to client}

\paragraph{ping} 
\paragraph{webid=123} sets webID of client to 123
\paragraph{status=Abc} sets the status message of the client to Abc
\paragraph{side=n} sets the side of the player to n (1 or 2)
\paragraph{toomanyplayers} 3rd player tries to join the game
\paragraph{nosuchaccount} there is no such account in the database - login failed
\paragraph{alreadyindb} creation failed - the username is taken
\paragraph{badpassword} login failed - wrong password
\paragraph{accountcreated} creation successful - user was added to database
\paragraph{loggedin} sent by server when 3rd player tries to join the game
\paragraph{playable} board is now playable
\paragraph{notplayable} board is not playable anymore
\paragraph{turnstart} turn starts for this player
\paragraph{turnend} turn ends for this player
\paragraph{duelended} duel has ended
\paragraph{youwon} this player has won
\paragraph{youlost} this player has lost
\paragraph{draw} this match has ended for this player with draw

\subsection{System messages that may be sent both ways}

\paragraph{disconnect} indicates that the other side has ended the communication, and disconnected (gentle way, because you can always cut your ethernet cable)

\section{Known issues}

I did not manage to establish a connection via Internet using this application. One machine, and LAN (including WLAN) connections were made, but no success with wide scale.

\end{document}
